---
title: "Twitter Final Writeup"
author: "Jonah Klein-Barton"
date: "April 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Overview

Our group was tasked with stealing twitter data from mayors of American cities over 30,000 people, putting it into a database, and analyzing it.The database can be found here: <https://wustl.app.box.com/file/289481874492>.



## **Visualization of data**

## Account Verification


I have succesfully embedded a plot and am proud of myself

```{r verif, echo=FALSE, warning=FALSE}
library(ggplot2)
load("mayor_Covariates.rds")
ggplot(data=mayor_Covariates)+geom_bar(mapping = aes(x = verified)) +labs(title = "Verificatation of Mayoral Twitter Accounts")
```

## Correlation between tweets and followers


```{r followers, echo=FALSE, warning=FALSE}
library(ggplot2)
load("mayor_Covariates.rds")
  #Followers between 0 and 10000
ggplot(data = mayor_Covariates) +
  geom_histogram(mapping = aes(x = followersCount), breaks = seq(0, 10000, by = 100)) +
  labs(title = "Follower Distribution for Followers <= 10,000")

  #More than 10000 followers
ggplot(data = mayor_Covariates) +
  geom_histogram(mapping = aes(x = followersCount), breaks = seq(10001, 300000, by = 10000)) + 
  labs(title = "Follower Distribution for Followers > 10,000")

```

## Correlation between tweets and followers

Another one

```{r tweet, echo=FALSE, warning=FALSE}
library(ggplot2)
load("mayor_Covariates.rds")
ggplot(data = mayor_Covariates, mapping = aes(x = log(statusesCount), y = log(followersCount))) + geom_point(na.rm = TRUE) +
  labs(title = "Log(Statuses) v. Log(followers) for Mayoral Accounts")
```



